---
title: "Morbid Curiosity, Anxiety & VANE"
author: "Brendan Jaghab & David Brocker"
format: 
  html:
    code-fold: true
    code-link: true
    code-tools: true
    toc: true
    toc-depth: 3
    toc-location: left
editor: visual
theme: 
  light: flatly
  dark: darkly
---

## Hypotheses:

**H1:** [Morbid Curiosity](https://uploads.strikinglycdn.com/files/bf7f54ad-91cf-49f6-b465-4afae046eb5b/Morbid%20Curiosity%20Scale%20instructions.pdf?id=3713948 "View MC Scale") should correlate and predict [Horror Typology](https://github.com/DavidBrocker/Morbid/blob/main/scales/The%20psychological%20benefits%20of%20scary%20play%20in%20three%20types%20of%20horror%20fans_preprint%20(6).pdf "View HT Scale").

**H2:** Morbid Curiosity should correlate with [anxiety](https://oml.eular.org/sysModules/obxOML/docs/id_150/State-Trait-Anxiety-Inventory.pdf#page=3 "View STAI"), using a two-tailed approach

**H3:** Morbidly Curious individuals are more likely to expose themselves to negative stimuli

**H4:** Anxious individuals should experience a decrease in anxiety after expose to (voluntary) negative stimuli

## Stimuli

+----------------------------------------------------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------+
| Negative                                                                                                                                                 | Positive                                                                              |
+==========================================================================================================================================================+=======================================================================================+
| An image of a man bleeding and screaming after a plane crash, surrounded by others running away from the crash.                                          | An image of a man screaming for the winning team of a basketball game.                |
|                                                                                                                                                          |                                                                                       |
| (**Body**)                                                                                                                                               |                                                                                       |
+----------------------------------------------------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------+
| An image of a third world country revolting against its military on the street                                                                           | An image of a third world country coming together in a moment of prayer.              |
|                                                                                                                                                          |                                                                                       |
| (**Violence**)                                                                                                                                           |                                                                                       |
+----------------------------------------------------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------+
| An image depicting an infamous, run-down haunted house                                                                                                   | An image depicting a newly built suburban home                                        |
|                                                                                                                                                          |                                                                                       |
| (**Paranormal**)                                                                                                                                         |                                                                                       |
+----------------------------------------------------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------+
| An image of a prisoner being prepared to be killed by the electric chair                                                                                 | An image of a prisoner being convicted not guilty of the charges against him.         |
|                                                                                                                                                          |                                                                                       |
| (**Violence**)                                                                                                                                           |                                                                                       |
+----------------------------------------------------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------+
| An image of a malnourished refugee in a third-world country                                                                                              | An image of a famous model, with a face of makeup, on a beach                         |
|                                                                                                                                                          |                                                                                       |
| (**Body**)                                                                                                                                               |                                                                                       |
+----------------------------------------------------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------+
| An image of a hunter carrying the severed, bloody head of a deer they just hunted.                                                                       | An image of a person carrying a basket of fresh-picked fruit.                         |
|                                                                                                                                                          |                                                                                       |
| (**Body**)                                                                                                                                               |                                                                                       |
+----------------------------------------------------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------+
| Watch a documentary explaining the murders of famous serial killer Dennis Nilsen, that includes his taped confession and how he carried out his murders. | Watch a documentary following the life of former Apple CEO, Steve Jobs.               |
|                                                                                                                                                          |                                                                                       |
| (**Mind**)                                                                                                                                               |                                                                                       |
+----------------------------------------------------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------+
| An image of a man putting a gun in a blood man's mouth as he pleads for mercy.                                                                           | An image of a man comforting another man that has just been attacked.                 |
|                                                                                                                                                          |                                                                                       |
| (**Violence**)                                                                                                                                           |                                                                                       |
+----------------------------------------------------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------+
| An image of a man shooting a polar bear in the arctic.                                                                                                   | An image of a man taking a photograph of a polar bear in the arctic.                  |
|                                                                                                                                                          |                                                                                       |
| (**Violence**)                                                                                                                                           |                                                                                       |
+----------------------------------------------------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------+
| Read a book that describes the rituals and magic beliefs of witches. (**Paranormal**)                                                                    | Read a book that describes various ways to improve your gardening skills.             |
+----------------------------------------------------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------+
| Read an FBI profile of serial killer John Dillinger explaining his murders and characteristics.                                                          | Read a profile describing the accomplishments of a well-known astronaut.              |
|                                                                                                                                                          |                                                                                       |
| (**Mind**)                                                                                                                                               |                                                                                       |
+----------------------------------------------------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------+
| An image of a man injecting heroin on the floor in a drug den.                                                                                           | An image of a man sleeping on the floor next to his two children.                     |
|                                                                                                                                                          |                                                                                       |
| (**Body**)                                                                                                                                               |                                                                                       |
+----------------------------------------------------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------+
| Listen to a podcast that focuses on infamous serial killers and their crimes.                                                                            | Listen to a podcast that comforts people by describing how to manage their anxieties. |
|                                                                                                                                                          |                                                                                       |
| (**Mind**)                                                                                                                                               |                                                                                       |
+----------------------------------------------------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------+
| An interactive video of how to play the spiritual game, Ouija. (**Paranormal**)                                                                          | An interactive video of how to play the board game, Monopoly.                         |
+----------------------------------------------------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------+
| An image depicting a witch's circle conducting a ritual.                                                                                                 | An image depicting a church.                                                          |
|                                                                                                                                                          |                                                                                       |
| (**Paranormal**)                                                                                                                                         |                                                                                       |
+----------------------------------------------------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------+
| Read an autobiography about the life of a serial killer.                                                                                                 | Read an autobiography about the life and accomplishments of Oprah Winfrey.            |
|                                                                                                                                                          |                                                                                       |
| **(Mind)**                                                                                                                                               |                                                                                       |
+----------------------------------------------------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------+

: Table 1. Stimuli Used in Study

### Data Processing

```{r}
# Load in Packages-------------------------------------------

library(dplyr, warn.conflicts = F) # Tidying data 
library(stringr) # String manipulation 
library(ggplot2) # Plotting 
library(purrr) # Handling lists and iterations 
library(tidytext) # Tidying text 
library(forcats) # Dealing with categories 
library(readxl) # Read Excel 
library(patchwork) # Plotting Multiple Graphs 
library(tidyr) # Reshaping 
library(huxtable, warn.conflicts = F) # Making nice tables 
library(ggcorrplot, warn.conflicts = F) # Correlation heatmap
library(skimr) # Continuous Data
library(janitor, warn.conflicts = F) # Cleaan names/Chi Square

# Establish Functions----------------------------------------

# Correlation Test Plot Function
correl_test <- function(data, col1,col2){

# Get Correlation: For x and y 
  d1 <- 
    data %>% 
    select({{col1}}) %>% 
    pull() 
  d2 <- 
    data %>% 
    select({{col2}}) %>% 
    pull()

# Store correlation test 
  ct <- cor.test(d1,d2)

# Store DF 
  degf <- ct$parameter %>% as.numeric()

# Store Confidence Intervals 
# First as numbers 
  ci <- round(ct$conf.int[1:2],2)

# Then as text: 95% CI [#,#] 
  cit <- paste0("95%CI[",ci[1],",",ci[2],"]")

# Store r value 
  rv <- round(ct$estimate,2)

# Plot and annotate 
  data %>%
    # Variable names are passed through with {{brackets}} 
    ggplot(aes({{col1}},{{col2}}))+ 
    geom_point() + # To get variable in plain text, use deparse(substitute(variable)) 
    labs(x = deparse(substitute(col1)), 
         y = deparse(substitute(col2)), 
         title = paste0( deparse( substitute(col1))," and ", deparse(substitute(col2))), 
    # Pull r value or anything else you want! 
    caption = paste0("r(",degf,")= ",rv," | ",cit)) +
    theme_minimal() + 
    theme( 
    # Center Plot 
    plot.title = element_text(hjust = .5, size = 16, face ="bold"))
}

# Standard Error Function
se <- function(x) { 
  se <- sd(x)/sqrt(length(x)) 
}

# Rescale MC and HT
# Morbid Curiosity
scale_six <- function(x) {(x/6)} 
# Horror Typology
scale_seven <- function(x) {(x/7)} 

# Discrete Scales
discrete_tab <- function(data,x,lab){
  name <- 
    data |> 
    dplyr::select({{x}}) |> 
    pull() 
  
  tab <- 
    name |> 
    tabyl() |> 
    dplyr::select(-(starts_with("val"))) |> 
    # Ignore Error for Now,,,
    adorn_pct_formatting(,,,percent) |> 
    rename_with(str_to_sentence) |> 
    hux() |> 
    theme_article() |> 
    set_align(everywhere,everywhere,".")

  # Change header row to Variable | | 
  tab[1,] <- c(str_to_sentence(x),"","")
  
  # Get Number of Rows
  to_in <- nrow(tab)
  
  tab[2:to_in,1] <- lab

  return(tab)
}

# Read and Clean Data----------------------------------------
 mcu <- read_excel("UpdatedMCdata.xlsx")

# Clean
 mcu_cln <- 
  mcu %>% 
  # Get participants who finished 
  filter(Finished == "1") %>% 
  # Get participants who consented 
  filter(`Consent?` == "1") %>% 
  # Remove unneeded columns 
  select(-DistributionChannel,-UserLanguage) %>% 
  # Clean variable names 
  rename_with(~gsub(" ","_",.x)) %>% 
  # Make Score Columns numeric 
  mutate_at(vars(SC0:SC14),as.numeric) %>% 
  # Remove SC0 and replace with scale name 
  rename( 
    Morbid_Curiosity_Overall = SC0, 
    Mind = SC1, 
    Body = SC2, 
    Violence = SC3,
    Paranormal = SC4, 
    Horror_Typology_Overall = SC5, 
    AJ = SC6, 
    WK = SC7, 
    DC = SC8, 
    Trait = SC9, 
    State_Pre = SC10, 
    Positive_Choice = SC11,
    Negative_Choice = SC12,
    PN_Choice = SC13, 
    State_Post = SC14) |>
  mutate(
    # Divide all MC Total Score by 24
    Morbid_Curiosity_Overall = Morbid_Curiosity_Overall/24,
    # Divide all HT Total Score by 19
    Horror_Typology_Overall = Horror_Typology_Overall/19 ) |>
    # Divide each MC Subscale Item by 6
    mutate_at(vars(Mind:Paranormal),scale_six) |> 
    # Divide each HT Subscale Item by 6
    mutate_at(vars(AJ:DC),scale_seven)
 
# Subset Scales
 mc_scaled <- 
  mcu_cln %>% 
  select(Morbid_Curiosity_Overall:State_Post)
```

## Demographics

```{r}
demo <- 
  mcu_cln |> 
  clean_names() |> 
  rename(
    major = major_of_study
  ) |> 
  select(gender,race,religion,major)

gen_lab <- 
  c("Male","Female", "Non-Binary","I prefer not to answer")


race_lab <- 
  c("Black or African American","White","Hispanic/Latino",
    "Asian","Multi-Racial","Other")

rel_lab <- 
  c("No Religion","Christian","Buddhist",
    "Hindu","Jewish","Muslim","Other","I prefer not to answer")

major_lab <- 
  c("Business Administration and Management", "Science, Technology, and Society",
    "Computer Programming", "Biology/Biological Sciences", "Applied Psychology", "Other")

# Get Tables for Gender, Age, Ethnicity, Politics, Race, and Education
gen <- discrete_tab(demo,"gender",gen_lab)

race <- discrete_tab(demo,"race",race_lab)

rel <- discrete_tab(demo,"religion",rel_lab)

major <- discrete_tab(demo,"major",major_lab)

# Build Table
gen |> 
  add_rows(race) |> 
  add_rows(rel) |> 
  add_rows(major) |> 
  # Add Header Row
  insert_row("Variable","N","Percent") |> 
  set_top_border(row = 1:3,1:3) |> 
  set_align(col = 1, value = "left") |>  
  set_align(1,1,"center") |> 
  set_caption("Table 2: Participant Demographics") |> 
  set_width(value = 1)
```

## Correlations

```{r}
# Clean variable name
x_var_names <- 
  c("Positive Choice", "Trait", "Pre State", 
    "Post State", "Dark Copers", "HT", 
    "Adrenaline Junkies", "Body","Negative Choice",
    "MC", "Mind", "Violence", 
    "Paranormal")

y_var_names <- 
  c("Violence", "Mind", "MC", 
    "Negative Choice", "Body", "Adrenaline Junkies", 
    "HT", "Dark Copers", "Post State", 
    "Pre State", "Trait", "Positive Choice","White Knuclers")

# Create Cor Matrix
heat_plot <- 
  mc_scaled |> 
  janitor::clean_names() |> 
  select(-pn_choice) |> 
  cor()

# Get p-value matrix
heat_pmat <- 
  heat_plot |>
  cor_pmat(sig.level = .05)

# Plot
heat_plot |> 
  ggcorrplot(
    type = "lower",
    hc.order = TRUE,
    p.mat = heat_pmat,
    #insig = "pch",
    lab = TRUE,
    method = "circle",
    lab_size = 2,
    colors = c("#780000","white","#003049"),
    legend.title = "Correlation") +
  scale_y_discrete(labels = y_var_names, position='right') +
  scale_x_discrete(labels = x_var_names, position = "bottom") + labs(caption = "Fig 1. Correlation Matrix Across all numeric variables. Crossed items represent non-significant correlations"
  ) +
  theme(axis.text.x = element_text(angle = 90, 
                                   hjust = 1),
        plot.caption = element_text(face = "italic",
                                    hjust = .2)) 
 
```

## State and Trait Comparisons

### Post vs. Pre

```{r}
t.test(mc_scaled$State_Post,mc_scaled$State_Pre, paired = T) |> 
  broom::tidy() |> 
     rename(
    t = statistic,
    p = p.value, 
    df = parameter,
    `mean difference` = estimate
  ) |> 
  hux() |> 
  theme_article() |> 
    set_caption("Table 3:  No significant difference (or decrease in anxiety)") |> 
  set_caption_pos("bottom")|> 
  set_width(value = 1)
```

### Pre vs. Trait

```{r}
t.test(mc_scaled$State_Pre,mc_scaled$Trait,paired = T) |> 
  tidy() |> 
    rename(
    t = statistic,
    p = p.value, 
    df = parameter,
    `mean difference` = estimate
  ) |> 
  hux() |> 
  theme_article() |> 
  set_caption("Table 4: Significant Difference between Pre Anxiety and Trait Anxiety
") |> 
  set_caption_pos("bottom")|> 
  set_width(value = 1)
```

### Post vs. Trait

```{r}
t.test(mc_scaled$State_Post,mc_scaled$Trait,paired = T) |> 
  broom::tidy() |> 
    rename(
    t = statistic, 
    p = p.value, 
    df = parameter,
    `mean difference` = estimate
  ) |> 
  hux() |> 
  theme_article() |> 
  set_caption("Table 5: Significant Difference between Posttest Anxiety and Overall") |> 
  set_caption_pos("bottom")|> 
  set_width(value = 1)
```

### STAI Measure: Low Anxiety vs. High Anxiety (Pre)

```{r}
mc_scaled %>% 
  select(State_Pre) %>% 
  mutate(Anxiety_Level = 
           ifelse(State_Pre> 40,"High Anxiety","Low Anxiety")) %>% 
  select(Anxiety_Level) |> 
  table() %>% 
  janitor::chisq.test() |> 
  broom::tidy() |> 
  rename(
    p = p.value, 
    df = parameter
  ) |> 
  mutate(
    method = "Chi-squared test"
  ) |> 
  hux() |> 
  theme_article() |> 
  set_caption("Table 6: There are significantly more 'high-anxiety' individuals compared to 'low'anxiety' individuals based on scores from the pretest measure of STAI") |> 
  set_caption_pos("bottom") |> 
  set_width(value = 1)
```

### STAI Measure: Low Anxiety vs. High Anxiety (Pre)

```{r}
mc_scaled %>% 
  select(State_Post) %>%
  mutate(Anxiety_Level = 
           ifelse(State_Post > 40,"High Anxiety","Low Anxiety")) %>%
  select(Anxiety_Level) %>%
  table() %>%
  janitor::chisq.test() |> 
  broom::tidy() |> 
   rename(
    p = p.value, 
    df = parameter
  ) |> 
  mutate(
    method = "Chi-squared test"
  ) |> 
  hux() |> 
  theme_article() |> 
    set_caption("Table 7: There are significantly more 'high-anxiety' individuals compared to 'low'anxiety' individuals based on scores from the posttest measure of STAI") |> 
  set_caption_pos("bottom")|> 
  set_width(value = 1)
```

### STAI Measure: Low Anxiety vs. High Anxiety (Trait)

```{r}
mc_scaled %>% 
  select(Trait) %>%
  mutate(Anxiety_Level = 
           ifelse(Trait > 40,"High Anxiety","Low Anxiety")) %>%
  select(Anxiety_Level) %>%
  table() %>%
  janitor::chisq.test() |> 
  broom::tidy() |> 
   rename(
    p = p.value, 
    df = parameter
  ) |> 
  mutate(
    method = "Chi-squared test"
  ) |> 
  hux() |> 
  theme_article() |> 
    set_caption("Table 8: There are significantly more 'high-anxiety' individuals compared to 'low'anxiety' individuals based on scores from the trait measure of STAI") |> 
  set_caption_pos("bottom")|> 
  set_width(value = 1)
```

```{r}
mc_scaled %>% 
  select(starts_with("State")) %>%
  rename_with(~gsub("State_","",.x)) |> 
  pivot_longer(cols = everything(),
               names_to = "time",
               values_to = "score") |>
  mutate(time = factor(time, levels = c("Pre", "Post"))) |>
  group_by(time) |> 
  summarize(mean = mean(score),
            se = se(score)) %>% 
  ggplot(aes(time,mean)) +
  geom_pointrange(aes(ymin = mean - se, ymax = mean + se)) + 
  scale_color_manual(values = c("red", "black")) +
  theme_minimal() + 
  labs(
    x = "\nTime",
    y = "Average\n",
    title = "Average State Anxiety Scores Before & After VANE\n",
    caption = "Fig. 2: No significant decrease in anxiety levels after exposure to VANE."
  ) +
  theme(plot.title = element_text(hjust = 0.5,
                                  face = "bold"),
        plot.caption = element_text(hjust = .2,
                                    face = "italic")) +
  ylim(30,46)


```

## Regressions

### Horror Typology as a function of Morbid Curiosity

```{r}

mc_ht.mod <- summary(lm(mc_scaled$Morbid_Curiosity_Overall ~ mc_scaled$Horror_Typology_Overall))

# Make Table
mc_tab <- 
  mc_ht.mod |> 
  huxreg(error_pos = "right",
         statistics = character(0)) |> 
  theme_article() |> 
  set_caption("Table 9: Model showing Morbid Curiosity Overall score as a predictor of Horror Typology Overall score") |> 
  set_caption_pos("bottom") |> 
  set_width(value = 1)

# Rename Model Name
mc_tab[1,2] <- "Model 1"
# Rename Model Coeficients 
mc_tab[2:3,1] <- c("Morbid Curiosity Overall","Horror Typology Overall")

mc_tab

# Plot the relationship
correl_test(mc_scaled, Morbid_Curiosity_Overall,Horror_Typology_Overall) +
  labs(x = "\nMorbid Curiosity Overall",
       y = "Horror Typology Overall\n",
       title = "Morbid Curiosity Overall and Horror Typology Overall\n",
       caption = "Fig 3. Correlation between Morbid Curiosity and Horror Typology") +
  geom_abline(color = "darkred") 
```

### MC Overall and Pre/Post

```{r}

mc_stai.mod <- 
  lm(Morbid_Curiosity_Overall~ State_Pre + State_Post,data = mc_scaled) %>%
  summary() 

mc_st_tab <- 
  mc_stai.mod |> 
  huxreg(error_pos = "right",
         statistics = character(0)) |> 
  theme_article() |> 
  set_caption("Table 10: Model showing Morbid Curiosity Overall score as a poor predictor of STAI Pre and Post") |> 
  set_caption_pos("bottom")|> 
  set_width(value = 1)

mc_st_tab[1,2] <- "Model 2"

mc_st_tab[2,1] <- c("Morbid Curiosity Overall")

mc_st_tab
  
```

## Negative & Positive Choice

```{r}
mc_scaled |>
  select(Positive_Choice, Negative_Choice) |>
  rename_with( ~ gsub("_Choice", "", .x, )) |>
  pivot_longer(cols = everything(),
               names_to = "Choice",
               values_to = "Picked") |>
  group_by(Choice) |>
  summarize(M = mean(Picked),
            SE = se(Picked)) |>
  ggplot(aes(Choice, M)) +
  geom_pointrange(aes(
    ymin = M - SE,
    ymax = M + SE,
    colour = Choice),
    fatten = 6,
    show.legend = F) +
  geom_line(group = 1) +
  theme_minimal() +
  labs(x = "\nChoice",
       y = "Average\n",
       title = "Average Choice of Stimuli Among Participants",
       caption = "Fig 4: Results indicate that on average, participants chose significantally more positive choices than negative choices.") +
  theme(axis.text = element_text(color = "black"),
        plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.title.y = element_text(size = 12),
        plot.caption = element_text(hjust = .2,
                                    face = "italic")) +
  scale_color_manual(values = c("darkgreen", "maroon"))
```

### Negative/Positive choice:

```{r}
choice_tt <- 
  t.test(mc_scaled$Negative_Choice,mc_scaled$Positive_Choice,
       paired = T,
       var.equal = T) 

choice_tt |> 
  tidy() |> 
  rename(
    t = statistic,
    p = p.value, 
    df = parameter,
    `mean difference` = estimate
  ) |> 
  hux() |> 
  theme_article() |> 
  set_caption("Table 11: Paired t-test showing participants chose significantally more positive items.") |> 
  set_caption_pos("bottom")|> 
  set_width(value = 1)
```

```{r}
mc_neg.mod <- 
  lm(data = mc_scaled, Morbid_Curiosity_Overall ~ Negative_Choice) |> 
  summary()

mc_neg.mod_tab <- 
  mc_neg.mod |> 
  huxreg(error_pos = "right",
         statistics = character(0)) |> 
  theme_article() |> 
  set_caption("Table 12: Model showing negative choice selection is accurately predicted by Morbid Curiosity Scale score") |> 
  set_caption_pos("bottom")|> 
  set_width(value = 1)

mc_neg.mod_tab[1,2] <- "Model 3"

mc_neg.mod_tab[2,1] <- "Morbid Curiosity Scale"

mc_neg.mod_tab
```

```{r}
#| message: false
mcu_cln |> 
  ggplot(aes(Morbid_Curiosity_Overall,Negative_Choice)) + 
  geom_point() + 
  theme_minimal() +
  geom_smooth(method = "lm") +
  labs(x = "\nMorbid Curiosity Score", 
       y = "Number of Negative Choices\n",
       caption = "Fig 5: Correlation between overall Morbid Curiosity and subsequent number of negative items picked: (r = .66, r2 = .43)") +
  theme(
    plot.caption = element_text(face = "italic",
                                hjust = .2),
     axis.text = element_text(color = "black")
  )
  
```

## Morbid Curiosity and Gender

```{r}
# Separate Gender and MC
gen_tt <- 
  mcu_cln %>% 
  select(Gender,Morbid_Curiosity_Overall) %>% 
  filter(Gender %in% 1:2) |> 
  mutate(Gender = 
           ifelse(Gender == 1,"Male","Female"))

t.test(gen_tt$Morbid_Curiosity_Overall~gen_tt$Gender) |> 
  tidy() |> 
    rename(
    t = statistic,
    p = p.value, 
    df = parameter,
    `mean difference` = estimate,
    Female = estimate1,
    Male = estimate2
  ) |> 
  hux() |> 
  theme_article() |> 
  set_caption("Table 12: Independent t-test shows no significant difference between scores on Morbid Curiosity Scale.") |> 
  set_caption_pos("bottom")|> 
  set_width(value = 1)

```

## Horror Typology and Gender

```{r}
genht_tt <- 
  mcu_cln %>% 
  select(Gender,Horror_Typology_Overall) %>% 
  filter(Gender %in% 1:2) |> 
  mutate(Gender = 
           ifelse(Gender == 1,"Male","Female")) 

t.test(genht_tt$Horror_Typology_Overall~genht_tt$Gender) |> 
  broom::tidy() |> 
    rename(
    t = statistic,
    p = p.value, 
    df = parameter,
    `mean difference` = estimate,
    Female = estimate1,
    Male = estimate2
  ) |> 
  hux() |> 
  theme_article() |> 
  set_caption("Table 13: Independent t-test shows no significant difference between scores on Horror Typology Scale.") |> 
  set_caption_pos("bottom")|> 
  set_width(value = 1)
```

## General Questions:

I consider myself to be morbidly curious.

```{r}
gen_quest <- 
  mcu_cln |> 
  clean_names() |> 
  rename(
    people_mc = a_d1, 
    self_mc = a_d2, 
    self_anx = a_d3,
    self_hor = a_d4
  ) |> 
  mutate_at(vars(people_mc:self_hor),as.numeric)

cor.test(gen_quest$self_mc,gen_quest$morbid_curiosity_overall) |> 
  tidy() |> 
  rename(
    df = parameter,
    p = p.value,
    t = statistic,
    r = estimate
  ) |> 
  hux() |> 
  theme_article() |> 
  set_caption("Table 14: Participants self rating of being morbidly curious was significantlly positivly correlated with morbid curiosity score") |> 
  set_caption_pos("bottom")|> 
  set_width(value = 1)
```

I consider myself to enjoy horror related content such Books, TV shows, Movies, Attractions, Podcast, etc.

```{r}
cor.test(gen_quest$self_hor,gen_quest$horror_typology_overall) |> 
    tidy() |>
    rename(
    df = parameter,
    p = p.value,
    t = statistic,
    r = estimate
  ) |> 
  hux() |> 
  theme_article() |> 
  set_caption("Table 15: Participants self rating of enjoying the horror genre was significantlly positivly correlated with horror typology score") |> 
  set_caption_pos("bottom")|> 
  set_width(value = 1)
```

I consider myself to be an anxious person.

```{r}
cor.test(gen_quest$self_anx, gen_quest$trait) |> 
    tidy() |>   
  rename(
    df = parameter,
    p = p.value,
    t = statistic,
    r = estimate
  ) |> 
  hux() |> 
  theme_article() |> 
  set_caption("Table 16: Participants self rating of anxiety was significantly positively correlated with the trait measure of anxiety.") |> 
  set_caption_pos("bottom")|> 
  set_width(value = 1)
```

I find people to be morbidly curious.

```{r}
t.test(gen_quest$people_mc, mu = 4, alternative = "greater") |> 
    broom::tidy() |> 
    rename(
    t = statistic,
    p = p.value, 
    df = parameter,
    `mean difference` = estimate
  ) |> 
  hux() |> 
  theme_article() |> 
  set_caption("Table 17: Single-sample t-test against the midpoint of 4 showed that people generally believe others to be morbidly curious.") |> 
  set_caption_pos("bottom") |> 
  set_width(value = 1)
```

## Descriptive Statistics of All Variables

```{r}

gen_quest |> 
  select(age,self_mc:trait_questionnaire_20,
         post_state_1:post_state_20,
         morbid_curiosity_overall:state_post,-pn_choice) |>
  mutate_all(as.numeric) |> 
  rename_at(vars(starts_with("state_")),~gsub("questionnaire_","",.x)) |> 
    rename_at(vars(starts_with("trait_")),~gsub("questionnaire_","",.x)) |> 
  relocate(state_pre, .before = trait) |> 
  relocate(state_post, .before = trait) |> 
  skim() |> 
  yank("numeric") |> 
  select(-starts_with("p"), 
         -n_missing, 
         -complete_rate) |> 
  rename( 
    variable = skim_variable,
    M = mean, 
    SD = sd
    ) |>
  mutate(
    `M(SD)` = paste0(round(M,2),"(",round(SD,2),")")) |> 
  select(-M,-SD) |>
  select(variable, `M(SD)`, hist) |> 
  hux() |> 
  theme_article() |> 
  set_width(value = 1) |> 
  set_align(col = 3, value = "center") |> 
  set_caption("Table 18: Descriptive statistics of all numeric variables.")
```
